Evaluation of the locality of the Mainline DHT

### 2014-05-29 paper.tex
updated paper

We consider this study very preliminary, further evaluations, with more powerful statistical analysis and more nodes, are needed in order to better quantify the locality properties and their performance implications.

>>>>

We consider this study very preliminary, further studies, with more powerful statistical analysis and more nodes, are needed in order to better quantify the locality properties and their performance implications.
